### 2016-10-05 Paper_v8.tex
Added Zeb1 ref

NF-$\kappa$B may also play an essential role of in the epithelial transformation.
NF-$\kappa$B may influence Snail expression through the AKT pathway and directly stabilize Snail activity \cite{Wu:2009cr}.  This is particularly important for integrating inflammation pathways, such as interleukin-6 (IL-6) and tumor necrosis factor-$\alpha$ (TNF-$\alpha$), which have been linked to EMT in pathological conditions \cite{Sullivan:2009bh}.
Other pathways such as Notch have also been shown to act synergistically with TGF-$\beta$ to express Slug in the developing embryo \cite{Niessen:2008nx}.
Lastly, while we have modeled classical protein signaling, we have not considered the role of regulatory RNAs on EMT.
There is growing evidence that microRNAs (miRNAs) play a strong role in EMT, where several miRNAs,
for example miR-21 and miR-31 are strongly associated with TGF-$\beta$ exposure \cite{Bullock:2012aa}, and Lu et al have suggested that
EMT is driven by a miR-34/SNAIL and miR-200/ZEB mutual-inhibition feedback circuit \cite{Lu:2013aa}.
Addressing missing structural components like these, could generate more insight into TGF-$\beta$ signaling and its role in phenotypic transformation.

>>>>

NF-$\kappa$B may also play an essential role of in the epithelial transformation.
NF-$\kappa$B may influence Snail expression through the AKT pathway and directly stabilize Snail activity \cite{Wu:2009cr}.  This is particularly important for integrating inflammation pathways, such as interleukin-6 (IL-6) and tumor necrosis factor-$\alpha$ (TNF-$\alpha$), which have been linked to EMT in pathological conditions \cite{Sullivan:2009bh}.
Other pathways such as Notch have also been shown to act synergistically with TGF-$\beta$ to express Slug in the developing embryo \cite{Niessen:2008nx}.
In addition, other important regulatory proteins such as ZEB1 should be added to the next generation model.
ZEB1 can activate the expression of mesenchymal genes such as collagens, smooth muscle actin and myosin, Vimentin while simultaneously contributing
to the repression of epithelial genes \cite{Liu:2008aa}.
Thus, ZEB1 can act in parallel to SNAIL and thus be an alternative to the canonical signaling paradigm presented here.
Lastly, while we have modeled classical protein signaling, we have not considered the role of regulatory RNAs on EMT.
There is growing evidence that microRNAs (miRNAs) play a strong role in EMT, where several miRNAs,
for example miR-21 and miR-31 are strongly associated with TGF-$\beta$ exposure \cite{Bullock:2012aa}, and Lu et al have suggested that
EMT is driven by a miR-34/SNAIL and miR-200/ZEB mutual-inhibition feedback circuit \cite{Lu:2013aa}.
Addressing missing structural components like these, could generate more insight into TGF-$\beta$ signaling and its role in phenotypic transformation.
